The revisited hidden weight bit function

### 2024-11-19 RevisedHiddenWeight.tex
modif comment, polish citations.

	\end{abstract}

@@

@@

Recent developments in stream ciphers have reignited interest in this function. The emergence of new applications for stream ciphers with filter functions on a larger number of variables—such as Hybrid Homomorphic Encryption (HHE)~\cite{CCS:NaeLauVai11}—has further emphasized the relevance of such functions. HHE requires Boolean functions that can be efficiently evaluated in an input-oblivious algorithm. For instance, several new binary stream ciphers have been proposed since 2016, including Kreyvium~\cite{JOC:CCFLNP18}, FLIP~\cite{EC:MJSC16}, Rasta~\cite{C:Rasta}, FiLIP~\cite{INDO:MCJS19}, and Dasta~\cite{TOSC:BeiLea20}. Currently, designs employing Boolean functions with more than one hundred variables as filters lead to HHE schemes with the best latency~\cite{INDO:HofMeaRic20,CCS:CDPP22,CIC:MeaParPei24}.

@@

@@

\pmnote{Preliminaries to adapt}

@@

The algebraic degree of multiples of a Boolean function is a crucial criterion for various attacks on stream ciphers that utilize a Boolean function as a filter. The well-known algebraic attack~\cite{EC:CouMei03} and fast algebraic attack~\cite{C:Courtois03} on filtered LFSRs have motivated the study of cryptographic properties such as algebraic immunity and fast algebraic immunity, investigated in numerous works (\eg \cite{C:HawRos04,ISC:JiaZhaWan13})).

@@

\begin{definition}[Fast algebraic immunity, \eg \cite{EC:ACGKMR06}]\label{def:fai} The fast algebraic immunity of a Boolean function $f\in \Bfn{n}$ is defined as $\FAI(f)=\min \{ 2 \AI(f), \min _{1 \le \degg(g)<\AI(f)} (\degg(g)+ \degg(fg))\}$.
\end{definition}

@@

@@

\pmnote{add a link to the public github or name of the name of this code in supplementary materials.}

\tsnote{Is on GitHub now: \texttt{Bounding\_Walsh.ipynb}}

@@

\section{Conclusion and open questions}
\pmnote{TODO or remove}

>>>>

\pmnote{add a small abstract, usually summary of introduction}		
	\end{abstract}

@@

\pmnote{proofread and modify introduction}

@@

Recent developments in stream ciphers have reignited interest in this function. The emergence of new applications for stream ciphers with filter functions on a larger number of variables—such as Hybrid Homomorphic Encryption (HHE)~\cite{CCS:NaeLauVai11}—has further emphasized the relevance of such functions. HHE requires Boolean functions that can be efficiently evaluated in an input-oblivious algorithm. For instance, several new binary stream ciphers have been proposed since 2016, including Kreyvium~\cite{JOC:CCFLNP18}, FLIP~\cite{EC:MJSC16}, Rasta~\cite{C:Rasta}, FiLIP~\cite{INDO:MCJS19}, Dasta~\cite{TOSC:BeiLea20} and Fasta~\cite{CTRSA:CidIndRad22}. 
Currently, designs employing Boolean functions with more than one hundred variables as filters lead to HHE schemes with the best latency~\cite{INDO:HofMeaRic20,CCS:CDPP22,CIC:MeaParPei24,eprint:AGHM24}.

@@

\pmnote{Add here the other notations we took if not explained locally or in the other parts of preliminaries}

@@

@@

The algebraic degree of multiples of a Boolean function is a crucial criterion for various attacks on stream ciphers that utilize a Boolean function as a filter. The well-known algebraic attack~\cite{EC:CouMei03} and fast algebraic attack~\cite{C:Courtois03} on filtered LFSRs have motivated the study of cryptographic properties such as algebraic immunity and fast algebraic immunity, investigated in numerous works (\eg \cite{FSE:Armknecht04,C:HawRos04,ISC:JiaZhaWan13})).

@@

\begin{definition}[Fast algebraic immunity, \eg \cite{EC:ACGKMR06}]\label{def:FAI} The fast algebraic immunity of a Boolean function $f\in \Bfn{n}$ is defined as $\FAI(f)=\min \{ 2 \AI(f), \min _{1 \le \degg(g)<\AI(f)} (\degg(g)+ \degg(fg))\}$.
\end{definition}

@@

\pmnote{Show me screenshots proving that 2 and 4 are correct}

@@

\pmnote{Create a public github with all the code (not the .tex) used relatively to the article. We will give this link for the public version. Fot the anonymous one we will not mention the git, and only add the files in supplementary material.}

%\pmnote{add a link to the public github or name of the name of this code in supplementary materials.}

%\tsnote{Is on GitHub now: \texttt{Bounding\_Walsh.ipynb}}

@@

\section{Conclusion and open questions}
\pmnote{add a small conclusion (summary of contributions), and elaborate on an opean question, for example on how the Cauchy estimate could be used for more families, other quadratic functions or more easily higher degree ones.}

\ifnum\anon=0
\section{Acknowledgments}
Pierrick Méaux was supported by the ERC Advanced Grant no. 787390.
\fi
